A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-10 paper.tex
Reduce contents in Related Work

%TODO: cite IOTAIndustryMarketplace
\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{The Publish/subscribe Communication Models Over Blockchain}
The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure pub/sub data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single point failure. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.

In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties. The subscribers request publisher directly and ask them to save a cache space for interested data. The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data. Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data. Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain. The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. The reputation system and the punishment rules against malicious acts of subscribers and publishers. Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides. Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.

The previous works contribute to different aspects of building a reliable pub/sub system over blockchain. However, a few work propose an overall thinking of the pub/sub system, which ensures the privacy of players, preserves data securely and make data trackable, which is a vital consideration for IoT and mobile computing across organizations, and even stimulates data economics.

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other. However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.

A. Colman et al. \cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold. Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.

Researches below adopt MAM as data storage and a secure data transmission layer. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading. Service requesters call for proposal of interested data and accept/reject proposals from service providers. After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens. This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}. Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.

O. Lamtzidis and J. Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm. The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality. Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players. And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM. With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.

@@

\subsubsection{Channel / Endpoint Creation}
The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in a Merkle signature scheme (MSS), and the "$-1$" is for announcing the ID of next channel or endpoint. A channel with height $n$ can create $2^n-1$ endpoints, and an endpoint with height $m$ can attach $2^m-1$ messages, therefore the capacity of a channel is $2^{nm}-2^n-2^m+1$ messages in total. The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required. In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data. The results are shown in Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create}. The time duration for each \textit{height} is the average time of running 100 rounds.

Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation. Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical. On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above. And the performance of PC remains acceptable even \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.

>>>>

%TODO: cite IOTAIndustryMarketplace
\section{Related Work}
\label{section:relatedWork}
G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. The data validation and traceability are achieved via Ethereum smart contract. But data is plaintext on blockchain that the system is not appropriate for sensitive data.

Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. Yet, without brokers, participants may need to reveal more sensitive information in order to communicate. By Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. With encrypted data contents storing on IPFS, and add the encrypted IPFS link to MAM for further exchange. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold, and enable trading and perform access control on Ethereum smart contract. However, the details of trading and interactions between providers and consumers are not illustrated in this paper.

The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the works above does not does not take into account the refund and unsubscribe mechanism of trading model.

@@

\subsubsection{Channel / Endpoint Creation}
The length of a channel or endpoint is $2^{height}-1$ where \textit{height} is the height of Merkle Hash Tree in a Merkle signature scheme (MSS), and the "$-1$" is for announcing the ID of next channel or endpoint. A channel with height $n$ can create $2^n-1$ endpoints, and an endpoint with height $m$ can attach $2^m-1$ messages, therefore the capacity of a channel is $2^{nm}-2^n-2^m+1$ messages in total. The greater the \textit{height} of MSS, the longer the channel/endpoint, however the higher the computational power required. In this task, both channel and endpoint creation are tested and the \textit{height} is set from 1 to 7 which is quite enough for data providers to upload data.

Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation. The time duration for each \textit{height} is the average time of running 100 rounds. Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical. On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above. And the performance of PC remains acceptable even \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
